Breast Cancer Diagnosis Classification Analysis

### 2022-12-08 powerpoint.rmd

@@

- Different measurements of each variable are correlated

- Relationship with Diagnosis visible for each measurement

```{r, fig.height=3, fig.width=4, fig.align='right', fig.pos='H'}
source("Danny's Analysis.R", echo = F, local = T)

>>>>

## Features

- 
-

@@

Different measurements of each variable are correlated

Relationship with Diagnosis visible for each measurement

```{r, fig.height=8, fig.width=12}
source("Danny's Analysis.R", echo = F, local = T)
